---
title: "Running the Glassdoor API"
author: "John Muschelli"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running the Glassdoor API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Glassdoor API Keys
In order to use the `glassdoor` package, you need an API key from Glassdoor (either https://www.glassdoor.com/developer/register_input.htm or click Get API key from  https://www.glassdoor.com/developer/index.htm).  

After that is done, you need to set up the API keys.  The keys are grabbed using 
```{r, eval = FALSE}
Sys.getenv("GLASSDOOR_PID")
Sys.getenv("GLASSDOOR_PAT")
```

so you can set these either using `~/.Renviron` (will work generally) or your standard `.profile` or `.bash_profile` (if you work with command lines).

I recommend `.Renviron` as that works well with RStudio.



# Calling the API


The function `have_glassdoor_tokens` is a little wrapper that allows you to check if you have both API keys set.  

For example, the below code will look for `employers` and search for `pharmaceuticals` within them.

```{r}
library(glassdoor)
if (have_glassdoor_tokens()) {
res = glassdoor_api(
  action = "employers",
  other = NULL,
  version = 1,
  format = "json",
  q = "pharmaceuticals")
}
```

The function used here is `glassdoor_api` which is the workhorse function of the package.   Generally, however, you probably want to use `glassdoor_job_stats`, `glassdoor_job_prog`, or `glassdoor_company`.

## Job Statistics 

Most of the defaults in `glassdoor_api` do not need to be set, but the User-Agent defaults to 
```{r}
agent = glassdoor_user_agent()
```

If you would like to change this, simply specify the `agent` argument in the `glassdoor` functions.

The job statistics specification can be found https://www.glassdoor.com/developer/jobsApiActions.htm#JobsStats. 

```{r}
if (have_glassdoor_tokens()) {
  res = glassdoor_job_stats(
    job_title = "sales associate",
    returnJobTitles = TRUE)
    head(res$content$response$jobTitles, 3)
}
```

## Job Progression 

The job statistics specification can be found https://www.glassdoor.com/developer/jobsApiActions.htm#JobProgression.

```{r}
job_name = "sales associate"
if (have_glassdoor_tokens()) {
  res = glassdoor_job_prog(
    jobTitle = job_name)
  head(res$content$response$results, 2)
}
```
which gives the percentage of transitions to another profession after being a `r job_name`


## Employers

You can also access information from employers from `glassdoor_company` or the 
duplicate function `glassdoor_employer`:

```{r}
if (have_glassdoor_tokens()) {
  res = glassdoor_company(
    q = "dropbox")
  print(res$content$response$employers[[1]]$ceo)
}
```